Experience shapes individual foraging specialization and success in a virtual predator-prey system

### 2023-10-25 manuscript/manuscript.Rmd
renamed files to remove chapter2 in title

---
title: "Experience shapes individual foraging specialization and success in a virtual predator-prey system"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: 
  - references1.bib
  - references2.bib
csl: ecology.csl
---

@@

\newpage
# INTRODUCTION {.unnumbered}

>>>>

---
title: "Experience shapes individual foraging specialization and success in a virtual predator-prey system"
output: 
  word_document:
    reference_docx: manuscript-styles.docx
    fig_caption: yes
bibliography: 
  - references1.bib
  - references2.bib
csl: ecology.csl
---

@@

# INTRODUCTION {.unnumbered}
